Sperm do not evolve to collaborate in female meiotic drive.

### 2014-04-28 writeup_and_notes/male_dependent_drive.tex
added male-genotype dependent results

Although the allelic identity of sperm could plausibly influence the outcome of female meiosis, 
	limited gene expression in sperm \citep[e.g.][]{Joseph2004}
	suggest a model where sperm influence female meiosis via expression of the fertilizing male's
	diploid genotype (perhaps due to proteins and RNAs packaged into the sperm).
This adds an additional parameter to the system -- the dominance of the drive enhancer in heterozygous males, 
	when this dominance is high, a narrow sliver of parameter space sustaining a polymorphism emerges (see Figure S\ref{Effect_of_dominance})
 presumably because positive frequency dependence diminishes with the dominance of the male effect driver.

>>>>

Although the allelic identity of sperm could plausibly influence the outcome of female meiosis, 
	limited gene expression in sperm \citep[e.g.][]{Joseph2004}
	suggest a model where sperm influence female meiosis via expression of the fertilizing male's
	diploid genotype (perhaps due to proteins and RNAs packaged into the sperm).
%GRAHAM I HAVE REWRITTEN THIS SECTION TO REFLECT MATHS AND MY PARAMETERIZATION. WE CAN WORK ON SYNCHING OUR NOTATION
%This adds an additional parameter to the system -- the dominance of the drive enhancer in heterozygous males, 
%	when this dominance is high, a narrow sliver of parameter space sustaining a polymorphism emerges (see Figure S\ref{Effect_of_dominance})
 %presumably because positive frequency dependence diminishes with the dominance of the male effect driver.
This male-genotype dependent model requires one additional parameter, as we exchange $d$ in the sperm dependent case for $d_{het}$ and $d_{hom}$ which describe the transmission of the drive allele in a heterozygous female mating with males heterozygous and homozygous for the self-promoting drive allele, respectively.  
When $d_{het}$ is large relative to $d_{hom}$, a narrow sliver of parameter space sustains a polymorphism (see Figure S\ref{Effect_of_dominance}), presumably because positive frequency dependence diminishes with the dominance of the male effect driver. 
As an analytical example, consider the case of male-genotype dependent deleterious recessive female driver 
	(assuming, as above, $w_{BB}=1-s$, and $w_{AA}=w_{AB}=1$). 
Here, a rare driver invades when $s<\frac{d_{het}-1/2}{d_{het}}$, and fixes when $s < d_{hom} - \frac{1}{2}$. 
Intermediate values of $s$, which represent a small proportion of parameter space can maintain a polymorphism.
